### 2018-05-09 doc/large_strain.tex
outline of the paper

@@

@@

>>>>

\section{Introduction}

TODO: elasticity and no matrix-free. fluids used a lot.

@@

\subsection{Linearization}

TODO: linearize and show how tangent look like.
Also show what it boils down in the case of small strain.

@@

\section{Matrix-free operator evaluation}

TODO[DD]: summary of what's happening, how operator is evaluated, what we do, what operations (determinant, etc), count number of FLOPS

\section{Numerical examples}

\subsection{Small strain linear elasticity}

TODO: summarize Mathias results (head and Cook's membrane)

TODO: switch head to quasi-static load instead of dynamics?

\subsection{Large strain Neo-Hook elasticity}

TODO: add new results from Cook's and some matrix-inclusion (matrix-pore).
Eliptical holes are easier as we don't need heterogeneous operator.

\section{Summary and Conclusions}

TODO: summarize results, good/bad, where can be applied,...
Bio-med fluid-structure ?
